### 2020-06-02 sc20_reviews/response.md

  * Our experiments are chosen to span the entire range of task granularities, from very efficient (large, and low overhead) to inefficient (small, and high overhead). METG naturally determines the point at which runtime overheads come to dominate application execution. What we report in the paper are empirical results: the limit of what each system can achieve. This is a lower bound, and generally, such systems will be efficient as long as tasks are at least that large. Also, as noted in the paper, clearly there are popular and widely used systems on both ends of this spectrum; therefore some classes of applications must be able to tolerate much larger task granularities.

  * For a specific example of an application where small task granularities are useful, see <https://ieeexplore.ieee.org/document/8948618>. Figure 2 shows that with a tile size of 1024 the algorithm achieves about 7 TFLOPS/s per GPU. The task executed on each tile is a straightforward matrix multiply, making it easy to determine the the FLOPS (and therefore task granularity): (2\*1024\*1024\*1024/10^9)/7000gflops = 307us.

## Reviewer 2

  * We added Section V-I. This section validates METG against time to solution. We show that it is possible to use METG, along with a single-node measurement of time to solution, to predict the strong scalability of a code (i.e., the point where it reaches 50% parallel efficiency, in terms of both time to solution, and node count). We find that we can predict time to solution (at 50% efficiency) to within a factor of 1.28X on average across 11 programming systems.

### 2020-06-02 sc20_reviews/response.md

  * We renamed Section VI.

  * We added the Deakin citation to our related work.

## Reviewer 4

  * Task Bench provides access to a large space of behaviors (kernel computation, load imbalance, shape of the task graph, number of dependencies and their structure, amount of data communicated, etc.). We agree that there are dimensions of this space that are not currently covered by Task Bench, and that are covered by specific mini-apps; we consider this a good direction for future work. In spite of this, the space covered by Task Bench today is already larger than the existing benchmarks, or any single mini-app. Moreover, Task Bench makes it dramatically easier to implement for a wide variety of systems, making comparative study feasible. We have added some clarifications to the introduction.

@@

  * We expanded Section VI.

## Reviewer 5

  * We agree that cross-validation with mini-apps is a good direction for future work, but that concrete benefits have already been demonstrated in the form of performance bugs found and fixed via Task Bench (see updated Section VI).

  * Whether dependencies are constructed ahead of time or on the fly is a feature of the programming model being used to implement of Task Bench, not a feature of Task Bench itself. E.g., Dask, PaRSEC, Regent and StarPU all construct the task graph on the fly. The core APIs shown in Table 3 are sufficient to do this, it is simply a matter of calling the right programming model APIs for each task. Listing 2 shows how we do this for MPI. All of our implementations are open source and will linked in the final paper.

  * We ensure that all core APIs are very efficient, making these checks low-cost so that there is no penalty to querying the APIs on the fly (if that is how the programming model is designed to be used).

@@

  * We added Section V-G.

  * Figure 11 is comparable to Figure 3. As described in the text, Figure 3 is generated from Figure 2 by computing, for each data point, efficiency and task granularity. These are derived metrics, resulting in a parametric graph. Intuitively, there is a data point per problem size, but task granularity does not necessarily decrease with problem size (due to overheads). Noise can also introduce variations in the measurements, especially at higher node counts, and particularly with MPI which uses a model of communicating sequential processes.

### 2020-06-02 1_introduction.tex
Tweaks for space.

%
% FIXME:  Move these two paragraphs out of the introduction and into one of the METG sections.
%
\zap{
Task Bench and METG address issues common in limit studies of runtime
systems for parallel and distributed programming. Such studies often
employ the metric \emph{tasks per second} (TPS), which is almost
universally measured with trivial (i.e., no) dependencies \cite{LegionTracing18, Canary16, Armstrong14}. While
phrased in terms of tasks, TPS can be measured for any system as long
as the application in question has identifiable units of work that run
to completion without interruption. TPS is an upper bound on
runtime-limited application throughput. But it is not a tight bound, as the
cost of non-trivial dependencies can be significant. This issue can be easily fixed by running non-trivial
configurations of Task Bench.

@@

% Performance issues:
% Chapel (communication performance, core pinning)
% Dask (asymptotic complexity of dask.delayed)
% PaRSEC (task pruning with non-trivial task graphs)
% Realm (DMA system overhead)
% TensorFlow (constant folding not parallel)

>>>>

%
% FIXME:  Move these two paragraphs out of the introduction and into one of the METG sections.
%
\zap{
Task Bench and METG address issues common in limit studies of runtime
systems for parallel and distributed programming. Such studies often
employ the metric \emph{tasks per second} (TPS), which is almost
universally measured with trivial (i.e., no) dependencies \cite{LegionTracing18, Canary16, Armstrong14}. While
phrased in terms of tasks, TPS can be measured for any system as long
as the application in question has identifiable units of work that run
to completion without interruption. TPS is an upper bound on
runtime-limited application throughput. But it is not a tight bound, as the
cost of nontrivial dependencies can be significant. This issue can be easily fixed by running nontrivial
configurations of Task Bench.

@@

% Performance issues:
% Chapel (communication performance, core pinning)
% Dask (asymptotic complexity of dask.delayed)
% PaRSEC (task pruning with nontrivial task graphs)
% Realm (DMA system overhead)
% TensorFlow (constant folding not parallel)
